Concurrent, Parallel Garbage Collection in Linear Time

### 2016-06-01 finaletd/mainintroduction.tex
changes

	\item First known garbage collectors that satisfy all the above-mentioned properties in both shared memory and distributed memory systems.

@@

	\item First known concurrent multi-collector reference counting based garbage collectors.

>>>>

	%\item First known garbage collectors that satisfy all the %above-mentioned properties in both shared memory and %distributed memory systems.

@@

	\item First known concurrent multi-collector shared memory garbage collector.
